---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}
body {
  font-family: arial;
}
h2{
color = #2C3E60;
}

```

## Analysing of video watching habits

This dynamic report consists of 22 reponses from the google form "Youtube videos you watch", it will show how different 22 responders engage with videos, and how long those videos were. It will also give out minimum, maximum and mean duration of those videos as well. \## Video Watching Trends Analysis

This report explores data on video watching habits, including video durations and engagement levels.

### Summary Statistics

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRiB1EB4fTMvrwnVmVaJmAXc8NUsulyPYhOpOZIEPkJedTi_UCODYUtlpoAaTycgW9SZPv3VkwKlqns/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    video_type = `What type of video did you watch?`,
    duration = `How long was the video?  (Must be a whole number minutes watched, e.g., 10).`,
    reason = `What made you decide to watch this video?`,
    interact = `Did you interact with the video (like, comment, share, subscribe)?`,
    engaging = `How engaging was the video?`
  )


min_duration <- min(latest_data$duration, na.rm = TRUE)
max_duration <- max(latest_data$duration, na.rm = TRUE)
mean_duration <- mean(latest_data$duration, na.rm = TRUE)
num_videos <- nrow(latest_data)

paste0("Total number of videos watched: ", num_videos, " minutes")
paste0("Minimum duration watched: ", min_duration, " minutes")
paste0("Maximum duration watched: ", max_duration, " minutes")
paste0("Average duration watched: ", round(mean_duration, 2), " minutes")


```



### Video Durations

```{r}
duration_plot <- latest_data %>%
  ggplot() + 
  geom_bar(aes(x = duration),
           fill = "blue") +
  labs(title = "Video Durations People Have Watched",
       subtitle = "Comparing video duration across different categories",
       x = "Video Duration (minutes)",
       y = "Number of Videos")

duration_plot
```


### Engagement Levels

```{r}
engagement_plot <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = engaging),
           fill = "darkgreen") +
  labs(title = "Engagement with Videos",
       x = "Engagement Level",
       y = "Count")

engagement_plot
```

